%-------------------------
% Resume - December 2025
%-------------------------

\documentclass[16pt,letterpaper]{extarticle}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\setmainfont{SF Pro Text}[
  BoldFont={SF Pro Text Bold},
  ItalicFont={SF Pro Text Italic}
]
% Semibold command for medium emphasis
\newfontfamily\sbfont{SF Pro Text Semibold}
\newcommand{\textsb}[1]{{\sbfont #1}}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\urlstyle{same}
\usepackage{xcolor}

% iOS-style text colors
\definecolor{primary}{gray}{0.0}      % Black - name, employers, sections
\definecolor{secondary}{gray}{0.25}   % Dark gray - roles, dates, locations
\definecolor{tertiary}{gray}{0.55}    % Medium gray - descriptions, bullets

% Light dotfill
\newcommand{\ldotfill}{{\dotfill}}
% Light horizontal rule
\newcommand{\lhrule}{{\rule{\linewidth}{0.2pt}}}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\setstretch{1.15}
\setlength{\parskip}{0pt}
\setlist[itemize]{nosep, leftmargin=1.5em}

% Footer with page numbers and date
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{{\fontsize{10pt}{12pt}\selectfont Page \thepage\ of \pageref{LastPage}}}
\fancyfoot[R]{{\fontsize{10pt}{12pt}\selectfont Fri Dec 27 2025}}

% Section formatting with underline
\titleformat{\section}{\LARGE\sbfont}{}{0em}{}[\vspace{-3pt}\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

% No paragraph indent
\setlength{\parindent}{0pt}

% Left-aligned text (no justification)
\raggedright

\begin{document}

%----------HEADER----------
\titleformat{name=\section,numberless}{\fontsize{28pt}{32pt}\selectfont\sbfont}{}{0em}{}[\vspace{-3pt}\titlerule]
\section*{Michael Vincent}
{\color{primary}\textsb{Software Engineer, Full Stack, Payments \& Infrastructure}} \\
{\color{primary}U.S. Citizen | Los Angeles, California | \href{https://mikevincent.dev}{mikevincent.dev}}


%----------EDUCATION----------
\section{Education}
{\textsb{The University of Texas at Tyler}}, {\color{secondary}Master of Science, Industrial Engineering}, {\color{tertiary}December 2015} \\
{\textsb{The Pennsylvania State University}}, {\color{secondary}Bachelor of Science, Linguistics}, {\color{tertiary}December 2011} \\
{\textsb{The Pennsylvania State University}}, {\color{secondary}Bachelor of Arts, Journalism}, {\color{tertiary}December 2011}

%----------EXPERIENCE----------
\section{Experience}
\begin{samepage}
{\large\textsb{Senior Software Engineer, Payments Infrastructure}} \\
{\color{secondary}PricewaterhouseCoopers (PwC), Los Angeles, California, United States} \\
{\color{tertiary}September 2024 to Present} \\[6pt]
{Founding engineer for "Capital One Databolt," a vaultless tokenization platform for payment and financial services providers.}\\
{\begin{itemize}
  \item Wrote Go APIs for licensing, authentication, and partner onboarding.
  \item Deployed with Docker and Helm to AWS EKS and Azure AKS.
  \item Added OpenTelemetry tracing; Zelle signed as first customer.
\end{itemize}}
\end{samepage}

\vspace{12pt}
\begin{samepage}
{\large\textsb{Relocation}} \\
{\color{secondary}Relocation} \\
{\color{tertiary}May 2024 to August 2024} \\[6pt]
{Relocated to Los Angeles, California, United States.}
\end{samepage}

\vspace{12pt}
\begin{samepage}
{\large\textsb{Software Engineering Manager, Infrastructure}} \\
{\color{secondary}Cubic Transportation Systems, San Diego, California, United States} \\
{\color{tertiary}October 2021 to April 2024} \\[6pt]
{Led a global team shipping fare systems for DC Metro, NYC MTA, BART, LA Metro, and Boston MBTA.}\\
{\begin{itemize}
  \item Built cloud infrastructure with Terraform, AWS, and GitHub Actions.
  \item Won multiple company awards for engineering excellence.
  \item Deployed mTLS security with Istio on Kubernetes.
\end{itemize}}
\end{samepage}

\vspace{12pt}
\begin{samepage}
{\large\textsb{Lead Senior Software Engineer}} \\
{\color{secondary}Cubic Transportation Systems, San Diego, California, United States} \\
{\color{tertiary}October 2019 to October 2021} \\[6pt]
{Built the "Cubic AI Chatbot" letting riders check card balances by phone and text.}\\
{\begin{itemize}
  \item Deployed chatbot on Azure with natural language processing.
  \item Built CI/CD for 20 Java apps with Jenkins, Docker, Helm, Vault, and Terraform.
  \item Built serverless pipelines with AWS Lambda and Azure Functions.
\end{itemize}}
\end{samepage}

\vspace{12pt}
\begin{samepage}
{\large\textsb{Senior Software Engineer}} \\
{\color{secondary}Cubic Transportation Systems, Washington, D.C., United States} \\
{\color{tertiary}May 2017 to October 2019} \\[6pt]
{First DevOps hire. Moved legacy infrastructure to containers and cloud for fare systems serving 10M+ daily riders.}\\
{\begin{itemize}
  \item Added Terraform, Kubernetes, and Docker to the organization.
  \item Passed PCI, SOC2, ISO, and SOX audits.
  \item Built Kubernetes monitoring with Prometheus and Grafana.
\end{itemize}}
\end{samepage}

\vspace{12pt}
\begin{samepage}
{\large\textsb{Senior Software Engineer, Infrastructure}} \\
{\color{secondary}EPAM Systems, Washington, D.C., United States} \\
{\color{tertiary}May 2016 to April 2017} \\[6pt]
{Promoted to senior backend engineer at digital UX agency building apps for enterprise clients.}\\
{\begin{itemize}
  \item Built Fannie Mae web app for mortgage lenders.
  \item Built Lockheed Martin Intranet on headless Drupal.
  \item Deployed microservices with Docker and Kubernetes 1.2.
\end{itemize}}
\end{samepage}

\vspace{12pt}
\begin{samepage}
{\large\textsb{Software Engineer}} \\
{\color{secondary}EPAM Systems, Washington, D.C., United States} \\
{\color{tertiary}May 2015 to April 2016} \\[6pt]
{Backend engineer on full-stack team building mobile apps and e-commerce platforms.}\\
{\begin{itemize}
  \item Built Poison Control mobile app and Canadian Tire e-commerce store.
  \item Moved PostgreSQL database to multi-tenant setup with zero downtime.
  \item Worked with Docker, Ansible, Jenkins, VMware ESXi, and Cisco ASA firewalls.
\end{itemize}}
\end{samepage}

%----------PROJECTS----------
\section{Projects}
\begin{samepage}
{\large\textsb{Io Pictures Corporation}} \\
{\color{tertiary}January 2022 to Present} \\[6pt]
{Founded California C Corporation engaged in buying, selling, and distributing licensed and acquired motion picture titles.}\\
{\begin{itemize}
  \item Sold rights to Tubi, Amazon, Apple, and Google through professional contacts.
  \item Negotiated domestic, international, publicity, and all-rights deals.
  \item Built digital distribution pipeline.
\end{itemize}}
\end{samepage}

\vspace{12pt}
\begin{samepage}
{\large\textsb{The Archive of American Radio, Inc.}} \\
{\color{tertiary}June 2025 to Present} \\[6pt]
{Founded California nonprofit for public-domain American radio drama, building the "Anthology" mobile app.}\\
{\begin{itemize}
  \item Built data processing pipelines and Cloudflare Workers APIs.
  \item Used Cloudflare D1, R2, Turso, Supabase, and Vercel.
  \item Developed custom OpenAI models for metadata extraction and search.
\end{itemize}}
\end{samepage}

\vspace{12pt}
\begin{samepage}
{\large\textsb{Quark's Outlines}} \\
{\color{tertiary}September 2024 to Present} \\[6pt]
{A learners guide to Python, published as a series of 100+ quick-read articles on DEV.to.}
\end{samepage}

%----------SKILLS----------
\section{Skills}
\textbf{Languages:} {\color{primary}Go, Python, JavaScript/TypeScript, Java, SQL, Bash, Rust} \\
\textbf{Cloud:} {\color{primary}AWS, Azure, Google Cloud Platform} \\
\textbf{Compute:} {\color{primary}Kubernetes, Docker, AWS EKS, Azure AKS, AWS Lambda, Azure Functions, GCP GKE} \\
\textbf{Storage:} {\color{primary}AWS S3, Cloudflare R2, Azure Blob, Redis, Kafka} \\
\textbf{Network:} {\color{primary}Istio, cert-manager, mTLS, Cloudflare Workers, API Gateway, Load Balancing} \\
\textbf{Databases:} {\color{primary}PostgreSQL, MySQL, MongoDB, Turso, Cloudflare D1, Supabase, DynamoDB} \\
\textbf{Infrastructure:} {\color{primary}Terraform, Helm, GitHub Actions, Jenkins, ArgoCD, Pulumi} \\
\textbf{AI/ML:} {\color{primary}OpenAI API, LangChain, Vector Databases, RAG, Embeddings} \\
\textbf{Observability:} {\color{primary}Prometheus, Grafana, OpenTelemetry, Datadog, PagerDuty} \\
\textbf{Security:} {\color{primary}Vault, OAuth2, JWT, PCI-DSS, SOC2, Zero Trust}

\end{document}
